### 2023-05-17 application.tex
sections

We may verify that  $\mathscr{S}=(S, \rightarrow, \leq)$ is $X$-resilient iff  $\mathscr{S}=(S, \rightarrow, \leq)$ is $\pred^*(X)$-resilient. The \emph{maximal $X$-resilient subsystem} of $(S,\rightarrow,\leq)$ is ....
\mathieu{ne pas oublier de mettre une définition ici}
Let us remark that given a WSTS $\mathscr{S}=(S, \rightarrow, \leq)$, one may construct many \emph{guard} systems where every transition $s \rightarrow s'$ of $\mathscr{S}$ is guarded by a (monotone) formula $\phi$ defined by the grammar $\phi ::= s \geq u \mid s' \geq u \mid \phi \vee \phi \mid \phi \wedge \phi$ where $u \in S$. Since guards restrict the original runs but don't create new ones, every guarded transition system $\mathscr{S'}$ is a subsystem of $\mathscr{S}$. Since these formula are upward-compatible, the guarded transition systems $\mathscr{S'}=(S, \rightarrow', \leq)$ are still WSTS.
%
For example, VASS allows such guards.
  %	\lor s' \geq x_2  	\lor...	\lor s' \geq x_p$ (facile dans les VASS et modèles habituels).

>>>>

We may verify that  $\mathscr{S}=(S, \rightarrow, \leq)$ is $X$-resilient iff  $\mathscr{S}=(S, \rightarrow, \leq)$ is $\pred^*(X)$-resilient. The \emph{maximal $X$-resilient subsystem} of $\mathscr{S}=(S,\rightarrow,\leq)$ is defined as $\mathscr{S}_X=(S,\rightarrow_X,\leq)$ where $\rightarrow_X$ is the largest restriction of $\rightarrow$ that insures that $\mathscr{S}_X$ is $X$-resilient.
\mathieu{ne pas oublier de mettre une définition ici}
Let us remark that given a WSTS $\mathscr{S}=(S, \rightarrow, \leq)$, one may construct many \emph{guard} systems where every transition $s \rightarrow s'$ of $\mathscr{S}$ is guarded by a (monotone) formula $\phi$ defined by the grammar $\phi ::= s \geq u \mid s' \geq u \mid \phi \vee \phi \mid \phi \wedge \phi$ where $u \in S$. Since guards restrict the original runs but don't create new ones, every guarded transition system $\mathscr{S'}$ is a subsystem of $\mathscr{S}$. Since these formula are upward-compatible, the guarded transition systems $\mathscr{S'}=(S, \rightarrow', \leq)$ are still WSTS.
%
For example, VASS allows such guards.
  %	\lor s' \geq x_2  	\lor...	\lor s' \geq x_p$ (facile dans les VASS et modèles habituels).
